\TESS Photometric Mapping of Surface Features on a Habitable-Zone Terrestrial Planet: Clouds, Oceans, and Continents

### 2019-03-23 tex/ms.tex
more references, better outline

% Author list
\author[0000-0002-0296-3826]{Rodrigo Luger}
\email{rluger@flatironinstitute.org}
\affil{Center~for~Computational~Astrophysics, Flatiron~Institute, New~York, NY}
%
\author[0000-0002-9328-5652]{Megan Bedell}
\affil{Center~for~Computational~Astrophysics, Flatiron~Institute, New~York, NY}

\begin{abstract}
The Transiting Exoplanet Survey Satellite (\TESS) mission is a targeted effort to detect planets smaller than Neptune around bright, nearby stars \citep{Ricker2015}. 
While \TESS is already enjoying great success with the discovery of many new worlds, the strongest signal in its data is typically ignored, as it lurks in the background of every camera pixel. 
In this work, we extract this signal and demonstrate that it is consistent with a terrestrial planet with a rotation period of 1 day. 
Using a spherical harmonic-based reflection model developed as an extension of the STARRY package \citep{Luger2018}, we are able to reconstruct the surface features of this rocky world. 
We recover a time-variable albedo map of the planet including persistent regions which we interpret as continental features and cloud banks. 
We argue that this planet represents the most promising detection of a habitable world to date, although the potential intelligence of any life on it is yet to be determined.
\end{abstract}

\keywords{ALIENS}

@@

A new source of precise photometry is the Transiting Exoplanet Survey Satellite (\TESS). 
Launched in April 2018, \TESS has... \todo{(summary of \TESS's capabilities, citations to planet discoveries etc)}

@@

@@

\subsection{Reflected-Light Mapping with STARRY}
\todo{(possibly make the gritty math details be an appendix?)}

@@

@@

@@

\acknowledgements{}
\software{Astropy, Matplotlib, Numpy, STARRY \citep{Luger2018}, TensorFlow}
% Bibliography
\pagebreak
\bibliography{bib}

>>>>

% Author list
\author[0000-0002-0296-3826]{Rodrigo Luger}
\email{rluger@flatironinstitute.org}
\affil{Center~for~Computational~Astrophysics, Flatiron~Institute, New~York, NY}
%
\author[0000-0002-9328-5652]{Megan Bedell}
\affil{Center~for~Computational~Astrophysics, Flatiron~Institute, New~York, NY}
%
\author{Roland K. Vanderspek}
\affil{Kavli Institute for Astrophysics and Space Research, Massachusetts Institute of Technology, Cambridge, MA}
%
\author{Christopher J. Burke}
\affil{Kavli Institute for Astrophysics and Space Research, Massachusetts Institute of Technology, Cambridge, MA}

\begin{abstract}
\todo{[maybe change first sentences to focus on planet mapping \& give the game away less?]}
The Transiting Exoplanet Survey Satellite (\TESS) mission is a targeted effort to detect planets smaller than Neptune around bright, nearby stars. 
While \TESS is already enjoying great success with the discovery of many new worlds, the strongest signal in its data is typically ignored, as it lurks in the background of every camera pixel. 
In this work, we extract this signal and demonstrate that it is consistent with a terrestrial planet with a rotation period of 1 day. 
Using a spherical harmonic-based reflection model developed as an extension of the STARRY package, we are able to reconstruct the surface features of this rocky world. 
We recover a time-variable albedo map of the planet including persistent regions which we interpret as continental features and cloud banks. 
We argue that this planet represents the most promising detection of a habitable world to date, although the potential intelligence of any life on it is yet to be determined.
\end{abstract}

\keywords{methods: data analysis, techniques: photometric, planets and satellites: oceans, planets and satellites: surfaces, planets and satellites: terrestrial planets}

@@

A new source of precise photometry is the Transiting Exoplanet Survey Satellite \citep[\TESS; ][]{Ricker2015}. 
Launched in April 2018, \TESS has... \todo{(summary of \TESS's capabilities, citations to planet discoveries etc)}

@@

\todo{(outlier rejection method, trim down to x number of high-SNR lightcurves for computational tractability)}

@@

While the astrophysical signal that we wish to analyze is present in all \todo{x} extracted lightcurves, its strength is modulated by time-variable systematics that are correlated but not identical across all sources. 
\todo{The observed lightcurves can be represented as... (systematics x Earthshine equation)}

We choose to model this systematic component using Pixel Level Decorrelation (PLD). \todo{(details, math, and a figure of the bases (possibly two-panel with comparison to telescope housekeeping variables?)}

\subsection{Reflected-Light Mapping with STARRY}

\todo{(brief recap of STARRY)}

\todo{(adapting STARRY to reflected light/variable illumination phase - possibly make the gritty math details be an appendix?)}

\todo{(time variability of surface features)}

@@

\todo{(priors, regularization, equation for the likelihood)}

\todo{(details of TensorFlow optimization)}

@@

\todo{(utility for \TESS background removal)}

@@

\acknowledgements{\todo{(Artist acknowledgement)} The authors gratefully acknowledge Dan Foreman-Mackey, David W Hogg, Ben Pope, \todo{and ...} for useful conversations. Crucial parts of this work were carried out at the TESS Data Workshop, hosted by Space Telescope Science Institute, and the Building Early Science with TESS Workshop, hosted by the University of Chicago.}
\facility{TESS}
\software{Astropy, Matplotlib, Numpy, STARRY \citep{Luger2019}, TensorFlow}
% Bibliography
\pagebreak
\bibliography{bib}
